---
title: "Beta_diversity"
output: html_notebook
---

# Insert the csv file 

```{r}
med <- read.csv("../Data/New_med_list.csv")
med
glimpse(med)

```

```{r}
str(med)
length(med$Genus)
```

```{r}
library(dplyr)
library(tidyverse)
```

#Split countries and get the unique taxa and Isolationsources for each of them

```{r}
s <- split(med, med$Country)

couspe_unique <- sapply

couiso_unique <- sapply(s, function(x){
  unique(x["Isolationsource"])
})
couiso_unique



```

# Select only habitat Pond and spread function
## Get beta diversity

```{r}
pondbeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 
pondbeta
summary(pondbeta)


#beta diversity
library(betapart)
  
pondbetapart <- pondbeta
pondbetapart[pondbetapart >= 1] <- 1
pondbetapart <- betapart.core(pondbetapart[, -1])
pondbetapart



```

# Select only habitat Lake and spread function
## Get beta diversity

```{r}

lakebeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 
#lakebeta <- lakebeta[, -2]
lakebeta
summary(lakebeta)


#beta diversity
library(betapart)
  
lakebetapart <- lakebeta
lakebetapart[lakebetapart >= 1] <- 1
lakebetapart <- betapart.core(lakebetapart[, -1])
lakebetapart

```

# Select only habitat Reservoir and spread function
## Get beta diversity

```{r}
resebeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Reservoir"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 
#lakebeta <- lakebeta[, -2]
resebeta
summary(resebeta)
str(resebeta)


#beta diversity
library(betapart)
  
resebetapart <- resebeta
#resebetapart[resebetapart >= 1] <- 1
resebetapart <- betapart.core(resebetapart[, -1])
resebetapart
```

```{r}
rivbeta <- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "River"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 
#lakebeta <- lakebeta[, -2]
rivbeta
summary(rivbeta)
str(rivbeta)


#beta diversity
library(betapart)
  
rivbetapart <- rivbeta
#resebetapart[resebetapart >= 1] <- 1
rivbetapart <- betapart.core(rivbetapart[, -1])
rivbetapart
```

# Alpha diversity of habitat pond

```{r}
library(dplyr)
library(tidyverse)

pondspr<- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Pond"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Isolationsource, N, fill = 0, convert = FALSE, sep = NULL)
pondspr

apply(pondspr[, -1] > 0, 2, sum)
```

# Alpha diversity of habitat Lake

```{r}
lakespr<- med %>%  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarise(N = n()) %>% 
  spread(Isolationsource, N, fill = 0, convert = FALSE, sep = NULL)
lakespr

apply(lakespr[, -1] > 0, 2, sum)
```

# Menhinick's index is simply the number of species (n) divided by the square-root of the total number of individuals (N).   D=n/√N



```{r}
n <- apply(lakespr[, -1]>0, 2, sum)
N <- apply(lakespr[, -1]>0, 2, sum)
Mehi <- n/sqrt(N)
Mehi
```

# Menhinick's index is simply the number of species (n) divided by the square-root of the total number of individuals (N).   D=n/√N

```{r}
n <- apply(pondspr[, -1]>0, 2, sum)
N <- apply(pondspr[, -1]>0, 2, sum)
Mehi <- n/sqrt(N)
Mehi
```

#Margalef's index is the number of species (n) minus 1 divided by the natural logarithm of the total number of individuals (N). D= (n−1)log(N)

```{r}
n <- apply(pondspr[, -1]>0, 2, sum)
N <- apply(pondspr[,-1]>0, 2, sum)
Margal <- (n-1)/log(N)
Margal
```


```{r}
lake_species <- med %>% 
  select(Currentname, Isolationsource) %>% 
  filter_all(any_vars(str_detect(., pattern = "Lake"))) %>% 
  group_by(Isolationsource) %>% 
  summarise(N = n()) %>% 
  arrange(desc(N))
lake_species <- head(lake_species, 10) %>%
  spread(Currentname, N, full = 0, convert = FALSE, sep = NULL)

```

# Compute total dissimilarity across all n sites, Sorensen and Jaccard indexes implementation of betapart package

```{r}
sore <- med %>% select(Isolationsource, Currentname, Order) %>% 
  filter(Order != " ") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 

sore_pa <- sore
sore_pa[sore_pa >=1] <- 1
sore_pa
s <-beta.multi(sore_pa[,-1],index.family = "sorensen")
s

j <- beta.multi(sore_pa[,-1], index.family = "jaccard")
j
```

```{r}
sore <- med %>% select(Isolationsource, Currentname, Order) %>% 
  filter(Order != " ") %>% 
  group_by(Isolationsource, Currentname) %>% 
  summarize(N = n()) %>% 
  spread(Currentname, N, fill = 0, convert = FALSE, sep = NULL) 


sore_pair <- sore
sore_pair[sore_pair >=1] <- 1
sore_pair

beta.pair(sore_pair[,-1], index.family = "sorensen")
beta.pair(sore_pair[, -1], index.family = "jaccard")

beta.sample(sore_pair[,-1], index.family = "sorensen", samples = 10)
```

```{r}
require(dismo)
```


